---
title: "ENVS-193DS_homework03"
author: "Anna Cote"
date: "2025-05-22"
format:
  html:
    toc: true # use this to display a table of contents
execute:
  message: false # use this to make sure messages don't show up
  warning: false # use this to make sure warnings don't show up
repository: https://github.com/annacote2026/ENVS-193DS_homework-03 # link to repository
---

```{r reading-in-packages}
library(tidyverse)
library(here)
library(flextable)
library(janitor)
library(readxl)
library(lubridate)
library(tidyr)
library(dplyr)
library(ggplot2)
```



# 1. Personal Data

a. I could calculate the frequency of each music genre for each given mood association (positive, negative, and neutral) by counting, because I listen to folk music often when I study, so I think the count for times I have listened to folk music while I'm feeling "neutral" (like focused or tired) will be higher than while I'm feeling "negatively".

b. 
```{r cleaning}
personal_data <- read_csv("data/193DS_Personal_Data.csv") |> # starting with my personal data frame
  clean_names()
```

```{r visualizing}
genre_mood_freq <- personal_data |> 
  count(genre, mood_association)
# count occurrences of genre and mood association

ggplot(genre_mood_freq, 
       aes(x = mood_association, 
           y = n,
           fill = genre)) + # assigning variables
  geom_bar(stat = "identity") + # telling R to use y-values I supply directly
  labs(
    title = "Frequency of Music Genres by Mood Association",
    x = "Mood Association",
    y = "Count",
    fill = "Genre" # rename axes, title, and legend
  ) + 
  theme_minimal() +
  scale_fill_brewer(palette = "Set2") + # choosing a new color palette for the bar chart
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) # angling the x-axis labels to be more readable
```

c. Figure 1. Comparison of the frequency that I listen to different music genres between negative, neutral, and positive mood associations, which were self-determined based on my emotions at the time of listening. Stacked bar chart shows individual counts of times listened to each genre during each mood association, as well as total count of times listened to music during each mood association. Folk music exhibited the highest overall listening frequency, and was also the most listened to genre during "negative" and "neutral" moods, whereas house music was the most listened to genre during "positive" moods. Data collected and recorded in personal music listening log (193DS_Personal_Data.xlsx).

d. 
```{r flextable}

```




